Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-04 paper/main.tex
Adds tikz file for figure 5
Updates

Our main contributions in this paper are as follows:
\begin{enumerate}
	\item We propose a novel measure of conditional association for mixed data
		based on canonical correlations. This measure of association
		generalizes some of the commonly used special case measures of 
		association to mixed data.
	\item Using this conditional association measure, we present a procedure to
		manually construct DAGs by ranking violation of implied CIs in the 
		model. This iterative procedure allows users to integrate their
		domain knowledge in the model construction procedure.
	\item Lastly, to allow researchers to easily apply this method on their
		datasets, we present a web-browser based interactive tool as well
		as implementation in a Python package.
\end{enumerate}

The rest of the paper is structured as follows. In
Section~\ref{sec:background}, we give a background on the commonly used
measures of association for various data types. In
Section~\ref{sec:mixed_association}, we present our generalized measure of
conditional association for mixed data. Section~\ref{sec:modification} provides
details on the procedure for using the measure of association for constructing
DAGs. Section~\ref{sec:web} presents our web-browser based tool and lastly in
Section~\ref{sec:empirical}, we show some empirical results to compare this
manual DAG construction approach to automated algorithms.

@@

\begin{figure}[t!]
	\centering
	\includegraphics[scale=0.3]{../code/fig5/llm_adult.png}
	\caption{DAG learned using the adult income dataset using an LLM (GEMINI-1.5-flash) as the expert.}
	\label{fig:adult_llm}
\end{figure}

>>>>

Our main contributions in this paper are as follows:
\begin{enumerate}
	\item We propose a novel measure of conditional association for mixed
		data based on canonical correlations
		(Section~\ref{sec:mixed_association}. This measure of
		association generalizes some of the commonly used special case
		measures of association to mixed data.
	\item Using this conditional association measure, we present a
		procedure to manually construct DAGs by ranking violation of
		implied CIs in the model (Section~\ref{sec:modification}. This
		iterative procedure allows users to integrate their domain
		knowledge in the model construction procedure.
	\item To allow researchers to easily apply this method on their
		datasets, we present a web-browser based interactive tool as well
		as implementation in a Python package (Section~\ref{sec:web}).
	\item Lastly, we compare the manual DAG construction method with automated
		causal discovery algorithms (Section~\ref{sec:empirical}).

\end{enumerate}

% The rest of the paper is structured as follows. In
% Section~\ref{sec:background}, we give a background on the commonly used
% measures of association for various data types. In
% Section~\ref{sec:mixed_association}, we present our generalized measure of
% conditional association for mixed data. Section~\ref{sec:modification} provides
% details on the procedure for using the measure of association for constructing
% DAGs. Section~\ref{sec:web} presents our web-browser based tool and lastly in
% Section~\ref{sec:empirical}, we show some empirical results to compare this
% manual DAG construction approach to automated algorithms.

@@

\begin{figure}[t!]
	\centering
	\includegraphics[page=1]{fig5.pdf}
	\caption{DAG learned using the adult income dataset using an LLM (GEMINI-1.5-flash) as the expert.}
	\label{fig:adult_llm}
\end{figure}
